---
title: "Simulation I: All Correlations Analysis"
author: "Tive Khumalo (M.A),  Sonja Winter (P.h.D), Wes Bonifay (P.h.D), Brian Keller (P.h.D) & Hyejin Shim (P.h.D)"
format: pdf
editor: visual
geometry: a2paper
---

## Simulation study I(B) analysis

- In this simulation we recreate the Preacher paper examples, i.e., the regression model and the causal model all with three variables. Its important to note that these models have equal number of parameters but different functional forms.

- We investigate the fitting propensities of each model from a total data space of one million random correlations (one million models).

- The following fit measures were used to assess the fitting propensity of each model: (a) log-likelihood, (b) comparative fit index (CFI), (c) standardized root mean squared residuals (SRMR), and (d) root mean square error of approximation (RMSEA).

- Lastly, we visualize our data space using a 3D figure.

```{r warning=FALSE, message=FALSE}
# loading the ockhamSEM library
library(ockhamSEM)

# loading the results
res_all_correlations <- readRDS(here::here("Online-Supplement","Data-Files" ,"study1_allcor.RDS"))
#summary(res_postive, probs = c(.025, .975))
```

- First, we assess the convergence rates for each model

```{r}
# extracting the fit propensity
fit <- res_all_correlations$fit_list

# proportions of models that did not converge/converged
prop.not <- sapply(fit, function(x) mean(is.na(x))) # did not converge
prop.con <- 1 - prop.not
```

- All of the models converged, i.e., the convergence rates were as follows, 100% for each respective model. Thus, its evident that we had no issues with convergence when we used positive correlations. We now look at the fitting propensities of each model across different fit indices thresholds. For CFI, we will use the following thresholds; .80, .85, .90, and .95. While for RMSEA and SRMR we will use the following thresholds; .20, .15, .10 and .05.

### Fitting propensity analysis

```{r}
# create function: input which model and which fit index to analyze
fit_propensity <- function(fit.propensity, model, fit.index = c('logl','cfi', 'srmr', 'rmsea'), threshold){
  
#'@param fit.propensity is the fit data for all models (a list of data frames or matrices)
#'@param model is the index of the model you want to analyze (e.g., 1 for fit[[1]])
#'@param fit.index is the fit statistic of interest (e.g., 'cfi')
#'@param threshold is the cutoff value
  
# number of observations
R <- nrow(fit.propensity[[model]])  
  
# number of decimal places
options(digits = 3)
  
# Check if the fit index is valid
if (!fit.index %in% c('cfi', 'srmr', 'rmsea')) {
    stop("Invalid fit index specified.")
}
  
# Extract the specific model's fit data
fit.data <- fit.propensity[[model]]
  
# Determine the column index corresponding to the fit index
fit.column <- which(colnames(fit.data) == fit.index)
  
# Error handling if fit index is not found
if (length(fit.column) == 0) {
    stop(paste("Fit index", fit.index, "not found in the data for the specified model."))
  }
  
if( fit.index == 'cfi'){
# Calculate the proportion of values greater than the threshold
  
# Frequency
res <- rev(table(fit.data[,fit.column] > threshold, useNA = 'always'))

# ensure all the trues are selected
 res_true <- ifelse('TRUE' %in% names(res), res['TRUE'], 0)

# Percentage
per <- (res_true / R) * 100

}else{  
  
# Frequency
res <- rev(table(fit.data[,fit.column] < threshold, useNA = 'always'))

# ensure all the trues are selected
res_true <- ifelse('TRUE' %in% names(res), res['TRUE'], 0)

# Percentage
per <- (res_true / R) * 100
    
}

# Return the result
results <- c(res_true, per)

# names
names(results) <- c('frequency', 'percentage')

return(results)
}

```

\newpage

**CFI**

```{r}
# results for model 1 (regression model)
# CFI > .85
cfi85.1 <- fit_propensity(fit.propensity = fit, model = 1, fit.index = 'cfi', threshold = .85)

# CFI > .80
cfi80.1 <- fit_propensity(fit.propensity = fit, model = 1, fit.index = 'cfi', threshold = .80)

# CFI > .90
cfi90.1 <- fit_propensity(fit.propensity = fit, model = 1, fit.index = 'cfi', threshold = .90)

# CFI > .95
cfi95.1 <- fit_propensity(fit.propensity = fit, model = 1, fit.index = 'cfi', threshold = .95)
```

We can interpret the following as follows:

- $49.2\%$ (492,113) of the 1,000,000 datasets had CFI values of .80 or greater.

- $42.9\%$ (429,486) of the 1,000,000 datasets had CFI values of .85 or greater.

- $35.4\%$ (354,122) of the 1,000,000 datasets had CFI values of .90 or greater.

- $25.4\%$ (254,003) of the 1,000,000 datasets had CFI values of .95 or greater.

```{r}
# results for model 2 (causal model)
# CFI > .85
cfi85.2 <- fit_propensity(fit.propensity = fit, model = 2, fit.index = 'cfi', threshold = .85)

# CFI > .80
cfi80.2 <- fit_propensity(fit.propensity = fit, model = 2, fit.index = 'cfi', threshold = .80)

# CFI > .90
cfi90.2 <- fit_propensity(fit.propensity = fit, model = 2, fit.index = 'cfi', threshold = .90)

# CFI > .95
cfi95.2 <- fit_propensity(fit.propensity = fit, model = 2, fit.index = 'cfi', threshold = .95)
```

We can interpret the following as follows:

- $36.5\%$ (365,146) of the 1,000,000 datasets had CFI values of .80 or greater.

- $31.3\%$ (313,464) of the 1,000,000 datasets had CFI values of .85 or greater.

- $24.4\%$ (254,099) of the 1,000,000 datasets had CFI values of .90 or greater.

- $18\%$ (179,573) of the 1,000,000 datasets had CFI values of .95 or greater.

- Overall, on average, model one had a higher fitting propensity than model two in terms of CFI across the different thresholds. This is surprising since the models have an equal number of parameters.

**SRMR**

```{r}
# results for model 1 (regression model)
# SRMR < .20
srmr20.1 <- fit_propensity(fit.propensity = fit, model = 1, fit.index = 'srmr', threshold = .20)

# SRMR < .15
srmr15.1 <- fit_propensity(fit.propensity = fit, model = 1, fit.index = 'srmr', threshold = .15)

# SRMR < .10
srmr10.1 <- fit_propensity(fit.propensity = fit, model = 1, fit.index = 'srmr', threshold = .10)

# SRMR < .05
srmr05.1 <- fit_propensity(fit.propensity = fit, model = 1, fit.index = 'srmr', threshold = .05)
```

We can interpret the following as follows:

- $47.1\%$ (471,197) of the 1,000,000 datasets had SRMR values of .20 or less.

- $36.2\%$ (361,754) of the 1,000,000 datasets had SRMR values of .15 or less.

- $24.5\%$ (245,037) of the 1,000,000 datasets had SRMR values of .10 or less.

- $12.4\%$ (123,811) of the 1,000,000 datasets had SRMR values of .05 or less.

```{r}
# results for model 2 (causal model)
# SRMR < .20
srmr20.2 <- fit_propensity(fit.propensity = fit, model = 2, fit.index = 'srmr', threshold = .20)

# SRMR < .15
srmr15.2 <- fit_propensity(fit.propensity = fit, model = 2, fit.index = 'srmr', threshold = .15)

# SRMR < .10
srmr10.2 <- fit_propensity(fit.propensity = fit, model = 2, fit.index = 'srmr', threshold = .10)

# SRMR < .05
srmr05.2 <- fit_propensity(fit.propensity = fit, model = 2, fit.index = 'srmr', threshold = .05)
```

We can interpret the following as follows:

- $70\%$ (700, 000) of the 1,000,000 datasets had SRMR values of .20 or less.

- $55.2\%$ (249,402) of the 1,000,000 datasets had SRMR values of .15 or less.

- $38.3\%$ (138,290) of the 1,000,000 datasets had SRMR values of .10 or less.

- $19.6\%$ (48,901) of the 1,000,000 datasets had SRMR values of .05 or less.

- Overall, on average, model two had a higher fitting propensity than model one in terms of SRMR across the different thresholds. This is not surprising since the models have an equal number of parameters. However, the different functional forms make model two flexible, such that it fits even random data well most of the time.

\newpage

**RMSEA**

```{r}
# results for model 1 (regression model)
# RMSEA < .20
rmsea20.1 <- fit_propensity(fit.propensity = fit, model = 1, fit.index = 'rmsea', threshold = .20)

# RMSEA < .15
rmsea15.1 <- fit_propensity(fit.propensity = fit, model = 1, fit.index = 'rmsea', threshold = .15)

# RMSEA < .10
rmsea10.1 <- fit_propensity(fit.propensity = fit, model = 1, fit.index = 'rmsea', threshold = .10)

# RMSEA < .05
rmsea05.1 <- fit_propensity(fit.propensity = fit, model = 1, fit.index = 'rmsea', threshold = .05)
```

We can interpret the following as follows:

- $25.3\%$ (253,074) of the 1,000,000 datasets had SRMR values of .20 or less.

- $19.3\%$ (193,017) of the 1,000,000 datasets had SRMR values of .15 or less.

- $13.3\%$ (132,867) of the 1,000,000 datasets had SRMR values of .10 or less.

- $7.52\%$ (75,201) of the 1,000,000 datasets had SRMR values of .05 or less.

```{r}
# results for model 2 (causal model)
# RMSEA < .20
rmsea20.2 <- fit_propensity(fit.propensity = fit, model = 2, fit.index = 'rmsea', threshold = .20)

# RMSEA < .15
rmsea15.2 <- fit_propensity(fit.propensity = fit, model = 2, fit.index = 'rmsea', threshold = .15)

# RMSEA < .10
rmsea10.2 <- fit_propensity(fit.propensity = fit, model = 2, fit.index = 'rmsea', threshold = .10)

# RMSEA < .05
rmsea05.2 <- fit_propensity(fit.propensity = fit, model = 2, fit.index = 'rmsea', threshold = .05)
```

We can interpret the following as follows:

- $20\%$ (200,000) of the 1,000,000 datasets had SRMR values of .20 or less.

- $15.2\%$ (152,230) of the 1,000,000 datasets had SRMR values of .15 or less.

- $10.5\%$ (104,525) of the 1,000,000 datasets had SRMR values of .10 or less.

- $5.93\%$ (59,254) of the 1,000,000 datasets had SRMR values of .05 or less.

- Overall, on average, model one had a higher fitting propensity than model one in terms of RMSEA across the different thresholds. This is surprising since when compared to the other fit measures model two overall had the highest fitting propensity, thus results are sort of counterintuitive to what we expected since model two is more flexible than model 1 thus we would expect it to have the highest fit propensities.

#### Cumulative plots

```{r fig.align='center'}
library(ggplot2)
# for the CFI with the cut-off set at  > .80, SRMR < .20 and RMSEA < .20
p1 <- plot(res_all_correlations, type='ecdf', whichfit = c('cfi', 'srmr', 'rmsea'), cutoff= c(.80, .20, .20), lower.tail = c(F, T, T),
      savePlot = T)

# for the CFI with the cut-off set at  > .85, SRMR < .15 and RMSEA < .15
p2 <- plot(res_all_correlations, type='ecdf', whichfit = c('cfi', 'srmr', 'rmsea'), cutoff= c(.85, .20, .20), lower.tail = c(F, T, T), savePlot = T)

# for the CFI with the cut-off set at  > .90, SRMR < .10 and RMSEA < .10
p3 <- plot(res_all_correlations, type='ecdf', whichfit = c('cfi', 'srmr', 'rmsea'), cutoff= c(.90, .10, .10), lower.tail = c(F, T, T),
      savePlot = T)

# for the CFI with the cut-off set at  > .95, SRMR < .05 and RMSEA < .05
p4 <- plot(res_all_correlations, type='ecdf', whichfit = c('cfi', 'srmr', 'rmsea'), cutoff= c(.95, .05, .05), lower.tail = c(F, T, T),
      savePlot = T)
```

```{r warning = FALSE, message = FALSE}
# loading the ggpubr
library(ggpubr)
```

```{r fig.align='center'}
# CFI plot
p.cfi <- p1[[1]]
# SRMR plot
p.srmr <- p1[[2]]
# RMSEA
p.rmsea <- p1[[3]]

# for the CFI with the cut-off set at  > .80 SRMR < .20 and RMSEA < .20
ggarrange(p.cfi, p.srmr, p.rmsea,
        labels = c('CFI > .80', 'SRMR < .20', 'RMSEA < .20'),
        font.label = list(size = 5))
```

```{r fig.align='center'}
# CFI plot
p.cfi <- p2[[1]]
# SRMR plot
p.srmr <- p2[[2]]
# RMSEA
p.rmsea <- p2[[3]]


# for the CFI with the cut-off set at  > .85 SRMR < .15 and RMSEA < .15
ggarrange(p.cfi, p.srmr, p.rmsea,
        labels = c('CFI > .85', 'SRMR < .15', 'RMSEA < .15'),
        font.label = list(size = 5))
```

```{r fig.align='center'}
# CFI plot
p.cfi <- p3[[1]]
# SRMR plot
p.srmr <- p3[[2]]
# RMSEA
p.rmsea <- p3[[3]]

# for the CFI with the cut-off set at  > .90 SRMR < .10 and RMSEA < .10
ggarrange(p.cfi, p.srmr, p.rmsea,
        labels = c('CFI > .90', 'SRMR < .10', 'RMSEA < .10'),
        font.label = list(size = 5))
```

```{r fig.align='center'}
# CFI plot
p.cfi <- p4[[1]]
# SRMR plot
p.srmr <- p4[[2]]
# RMSEA
p.rmsea <- p4[[3]]


# for the CFI with the cut-off set at  > .95 SRMR < .05 and RMSEA < .05
ggarrange(p.cfi, p.srmr, p.rmsea,
        labels = c('CFI > .95', 'SRMR < .05', 'RMSEA < .05'),
        font.label = list(size = 5))
```

#### Euler plots

```{r fig.align='center'}
library(ggplot2)
# for the CFI with the cut-off set at  > .80, SRMR < .20 and RMSEA < .20
p11 <- plot(res_all_correlations, type='euler', whichfit = c('cfi', 'srmr', 'rmsea'), cutoff= c(.80, .20, .20), lower.tail = c(F, T, T),
        savePlot = T)

# for the CFI with the cut-off set at  > .85, SRMR < .15 and RMSEA < .15
p21 <- plot(res_all_correlations, type='euler', whichfit = c('cfi', 'srmr', 'rmsea'), cutoff= c(.85, .15, .15), lower.tail = c(F, T, T),
      savePlot = T)

# for the CFI with the cut-off set at  > .90, SRMR < .10 and RMSEA < .10
p31 <- plot(res_all_correlations, type='euler', whichfit = c('cfi', 'srmr', 'rmsea'), cutoff= c(.90, .10, .10), lower.tail = c(F, T, T),
      savePlot = T)

# for the CFI with the cut-off set at  > .95, SRMR < .05 and RMSEA < .05
p41 <- plot(res_all_correlations, type='euler', whichfit = c('cfi', 'srmr', 'rmsea'), cutoff= c(.95, .05, .05), lower.tail = c(F, T, T),
      savePlot = T)
```

```{r fig.align='center'}
# CFI plot
p.cfi <- p11[[1]]
# SRMR plot
p.srmr <- p11[[2]]
# RMSEA
p.rmsea <- p11[[3]]


# for the CFI with the cut-off set at  > .80, SRMR < .20 and RMSEA < .20
ggarrange(p.cfi, p.srmr, p.rmsea,
        labels = c('CFI > .80', 'SRMR < .20', 'RMSEA < .20'),
        font.label = list(size = 10), nrow = 1)
```

```{r fig.align='center'}
# CFI plot
p.cfi <- p21[[1]]
# SRMR plot
p.srmr <- p21[[2]]
# RMSEA
p.rmsea <- p21[[3]]

# for the CFI with the cut-off set at  > .85, SRMR < .15 and RMSEA < .15
ggarrange(p.cfi, p.srmr, p.rmsea,
        labels = c('CFI > .85', 'SRMR < .15', 'RMSEA < .15'),
        font.label = list(size = 10), nrow = 1)
```

```{r fig.align='center'}
# CFI plot
p.cfi <- p31[[1]]
# SRMR plot
p.srmr <- p31[[2]]
# RMSEA
p.rmsea <- p31[[3]]

# for the CFI with the cut-off set at  > .90, SRMR < .10 and RMSEA < .10
ggarrange(p.cfi, p.srmr, p.rmsea,
        labels = c('CFI > .90', 'SRMR < .10', 'RMSEA < .10'),
        font.label = list(size = 10), nrow = 1)
```

```{r fig.align='center'}
# CFI plot
p.cfi <- p41[[1]]
# SRMR plot
p.srmr <- p41[[2]]
# RMSEA
p.rmsea <- p41[[3]]

# for the CFI with the cut-off set at  > .95, SRMR < .05 and RMSEA < .05
ggarrange(p.cfi, p.srmr, p.rmsea,
        labels = c('CFI > .95', 'SRMR < .05', 'RMSEA < .05'),
        font.label = list(size = 10), nrow = 1)
```

### Visualizing the Data space

```{r}
# extracting the correlation matrices
cors <- res_postive$R 
# extracting the values in the lower triangle and transposing them
cors_set <- t(sapply(cors, FUN = function(x) x[lower.tri(x)]))  

# saving the above values as a data frame
cors_set <- as.data.frame(cors_set)
# calculating the distance in sqrt(x^2+y^2+z^2) (Euler Distance)
cors_set$dists02 <- apply(cors_set, 1, function(x) sqrt(x[1]^2 + x[2]^2 + x[3]^2)) 

# loading this package
library(plotly) 


fig10 <- plot_ly(cors_set[1:10,], x = ~V1, y = ~V2, z = ~V3,
                 marker = list(color = ~dists02, colorscale = 'Viridis')) %>% 
  add_markers(marker = list(opacity = .7, size = 4)) %>%
  layout(scene = list(xaxis = list(title = "r1", range = c(-1,1)),
                      yaxis = list(title = "r2", range = c(-1,1)),
                      zaxis = list(title = "r3", range = c(-1,1)),
                      aspectmode='cube'))

```

**Interpretation: Regarding Study 1, we replicate the finding that model 2 has higher FP based on SRMR (with all cor or positive cor). But, at least based on the figure that looks at data space size, it seems like that pattern is not consistent for CFI and RMSEA. When we just look at positive correlations, model 2 has higher FP based on CFI ≥ .95 and RMSEA \< .10. But when we look at positive and negative correlations, model 1 has higher FP based on CFI ≥ .95 and RMSEA \< .10 .Does my interpretation match what you've found by looking at the ECDF and Euler plots? It would be good if we both see the same pattern. It might also be good to check how the data space size results change with alternative cutoff values (I used CFI ≥.95, RMSEA \< .10, SRMR \<.08, which are based on the guidelines in our SEM textbook).**
