---
title: "Simulation III: Positive Correlations Analysis"
author: "Tive Khumalo (M.A),  Sonja Winter (Ph.D), Wes Bonifay (Ph.D), Brian Keller (Ph.D) & Hyejin Shim (Ph.D)"
format: pdf
editor: visual
geometry: a2paper
---

```{r}
# loading the data set
load(here::here("Online-Supplement","Data-Files", "output_poscor_all_3.RData"))
```

- Since we have 48 models we will first assess convergence across all 48 models using a simple function that is shown below.

```{r}
# loading the tidyverse package
library(tidyverse)

# non-convergence
non_con <- sapply(output, function(x) mean(is.na(x)))

# convergence 
con <- 1 - non_con

# Grid of conditions that we can use for post-processing ----
study3_conditions <- expand.grid(model = 1:3, 
                                 bounds = c("none", "pos.var"),
                                 ident = c("refmarker", "unitvar"),
                                 mlit = c(150, 1500),
                                 conv = c("F", "T"))

# models as factors
study3_conditions$model <- factor(study3_conditions$model)
```

```{r warning=FALSE, message=FALSE}
# merging
results_one <- cbind(study3_conditions, con, non_con)


# loading the tidyverse package
library(tidyverse)

# average convergence and non-convergence
results_one %>%
  group_by(model) %>%
  summarize(
  # average convergence
  avg_con = mean(con) * 100,
  # average non-convergence
  avg_non_con = mean(non_con) * 100
  )
```

- Now we will look at the convergence rates across our conditions.

```{r}
# average convergence and non-convergence
results_one %>%
  group_by(model, bounds, ident, mlit, conv) %>%
  summarize(
  # average convergence
  avg_con = mean(con) * 100,
  # average non-convergence
  avg_non_con = mean(non_con) * 100, .groups = 'keep'
  ) %>%
  filter(avg_con != 1.0 & avg_non_con != 0)
```

```{r cells with low convergence}
# filter models with convergences lower or equal to 94%
results_one |>
  select(-non_con) |>
  filter(con <= .94)

```

```{r}
# first condition
row_1 <- study3_conditions[1,]
# first data frame in output
tab_1 <- output[[1]]

# merging
tab_merged <- bind_cols(tab_1, row_1)
```

```{r}
# number of conditions
num_con <- nrow(study3_conditions)

# number of data frames in the output
k <- length(output)

# check if the above is equal
if(k != num_con){
  stop('error k and num_con should be the same')
}

# container to save the results
output_conditions <- list()

for(i in 1:k){
  output_conditions[[i]] <- bind_cols(output[[i]], study3_conditions[i,])
  
}



# saving the dataset#
save(output_conditions, file = here::here("Online-Supplement","Data-Files","output_poscor_3_all_conditions.RData"))
```

```{r}
# loading the data
load(here::here("Online-Supplement","Data-Files", "output_poscor_3_all_conditions.RData"))
```

### Fitting propensity analysis

```{r}
fitting_prop <- function(Data, fit.index = c('logl', 'cfi', 'srmr', 'rmsea'), threshold, conditions = study3_conditions){
  
# Number of observations
R <- nrow(Data[[1]])  
  
# Container for results  
res <- list()

# Store percentage values 
per <- list()

# Storing frequencies
freq <- list()
  
# Fit indices loop
for (i in seq_along(Data)) {  
  
res[[i]] <- Data[[i]]
    
# Matching the column index for fit index
fit.column <- which(colnames(res[[i]]) == fit.index)
    
if (length(fit.column) == 0) {
 stop(paste("Column", fit.index, "not found in dataset", i))
}
    
if (fit.index == "cfi") { 
  
# Calculate the proportion of values greater than the threshold
  results <- rev(table(res[[i]][,fit.column] > threshold, useNA = 'always'))
  
}else if (fit.index %in% c('srmr','rmsea')){  
  
# Calculate the proportion of values less than the threshold
  results <- rev(table(res[[i]][,fit.column] < threshold, useNA = 'always'))

# log-likelihood  
} else {
  
  # Calculate the proportion of values less than the threshold
  results <- rev(table(res[[i]][,fit.column] > threshold, useNA = 'always'))
  
}    

# Ensure "TRUE" exists in results; otherwise, assign 0
results_true <- ifelse("TRUE" %in% names(results), results['TRUE'], 0)
    
# Saving the frequencies
freq[[i]] <- results_true
    
# Calculate percentages and saving them
per[[i]] <- (results_true / R) * 100
  }
  
# Return the results as data frame
dat <- data.frame('frequency' = unlist(freq), 'percentages' = unlist(per))

# adding the conditions
dat <- bind_cols(dat, conditions)

# output
return(dat)

}
```

\newpage

**CFI**

```{r}
# cfi > .50
cfi_5 <- fitting_prop(Data = output_conditions, fit.index = 'cfi', threshold = .5, models = 1)
```

```{r}
# cfi > .45
cfi_45 <- fitting_prop(Data = output_conditions, fit.index = 'cfi', threshold = .45)
```

```{r}
# cfi > .40
cfi_40 <- fitting_prop(Data = output_conditions, fit.index = 'cfi', threshold = .40)
```

\newpage

**SRMR**

```{r}
# srmr < .10
srmr_10 <- fitting_prop(Data = output_conditions, fit.index = 'srmr', threshold = .10)
```

```{r}
# srmr < .09
srmr_09 <- fitting_prop(Data = output_conditions, fit.index = 'srmr', threshold = .09)
```

```{r}
# srmr < .08
srmr_08 <- fitting_prop(Data = output_conditions, fit.index = 'srmr', threshold = .08)
```

```{r}
# srmr < .05
srmr_05 <- fitting_prop(Data = output_conditions, fit.index = 'srmr', threshold = .05)
```

\newpage

**RMSEA**

```{r}
# rmsea < .30
rmsea_30 <- fitting_prop(Data = output_conditions, fit.index = 'rmsea', threshold = .30)
```

```{r}
# rmsea < .27
rmsea_27 <- fitting_prop(Data = output_conditions, fit.index = 'rmsea', threshold = .27)
```

```{r}
# rmsea < .25
rmsea_25 <- fitting_prop(Data = output_conditions, fit.index = 'rmsea', threshold = .25)
```

\newpage

### Tables

**CFI**

```{r}
# loading gt
library(gt)

# wider table
cfi_50_wider <- cfi_5 %>%
  select(- frequency) %>% # removing the frequency column
  pivot_wider(names_from = c(conv, mlit),
  values_from = percentages, names_expand = T) %>%
  relocate(model) %>% # interchanging the first column with the model column
  mutate(
  ident = as.character(ident),
  model = as.character(model), 
  bounds = paste0('Bounds: ', bounds)
  )
```

```{r}
# the actual names
actual_names <- colnames(cfi_50_wider)

# new names
new_names <- actual_names %>%
  str_remove('(F|T)_') %>%
  str_to_title()

names(new_names) <- actual_names
```

```{r}
# table
cfi_50_table <- cfi_50_wider %>%
  gt(groupname_col = 'model', rowname_col = 'ident') %>% 
  cols_label(.list = new_names) %>%
  tab_spanner(
    label = md('T'),
    columns = contains('T')
  ) %>%
  tab_spanner(
    label = md('F'),
    columns = contains('F')
  ) %>%
  tab_spanner(
    label = md('Forced Convergence'),
    columns = contains('T') | contains('F')
  ) %>%
  cols_align(
    align = 'left',
    columns = c(where(is.factor), where(is.character))
  ) %>%
  cols_label(
  bounds = 'Maximum Iterations'  
  )%>%
  fmt_number(decimals = 3)
```

```{r}
cfi_50_table
```

```{r}
gt::gtsave(data = cfi_50_table, filename = 'cfi_50_table.docx', path="Tables")
```

```{r}
# wider table
cfi_45_wider <- cfi_45 %>%
  select(- frequency) %>% # removing the frequency column
  pivot_wider(names_from = c(conv, mlit),
  values_from = percentages, names_expand = T) %>%
  relocate(model) %>% # interchanging the first column with the model column
  mutate(
  ident = as.character(ident),
  model = as.character(model), 
  bounds = paste0('Bounds: ', bounds)
  )
```

```{r}
# the actual names
actual_names <- colnames(cfi_45_wider)

# new names
new_names <- actual_names %>%
  str_remove('(F|T)_') %>%
  str_to_title()

names(new_names) <- actual_names
```

```{r}
# table
cfi_45_table <- cfi_45_wider %>%
  gt(groupname_col = 'model', rowname_col = 'ident') %>% 
  cols_label(.list = new_names) %>%
  tab_spanner(
    label = md('T'),
    columns = contains('T')
  ) %>%
  tab_spanner(
    label = md('F'),
    columns = contains('F')
  ) %>%
  tab_spanner(
    label = md('Forced Convergence'),
    columns = contains('T') | contains('F')
  ) %>%
  cols_align(
    align = 'left',
    columns = c(where(is.factor), where(is.character))
  ) %>%
  cols_label(
  bounds = 'Maximum Iterations'  
  )%>%
  fmt_number(decimals = 3)
```

```{r}
cfi_45_table
```

```{r}
gt::gtsave(data = cfi_45_table, filename = 'cfi_45_table.docx', path="Tables")
```

```{r}
# wider table
cfi_40_wider <- cfi_40 %>%
  select(- frequency) %>% # removing the frequency column
  pivot_wider(names_from = c(conv, mlit),
  values_from = percentages, names_expand = T) %>%
  relocate(model) %>% # interchanging the first column with the model column
  mutate(
  ident = as.character(ident),
  model = as.character(model), 
  bounds = paste0('Bounds: ', bounds)
  )
```

```{r}
# the actual names
actual_names <- colnames(cfi_40_wider)

# new names
new_names <- actual_names %>%
  str_remove('(F|T)_') %>%
  str_to_title()

names(new_names) <- actual_names
```

```{r}
# table
cfi_40_table <- cfi_40_wider %>%
  gt(groupname_col = 'model', rowname_col = 'ident') %>% 
  cols_label(.list = new_names) %>%
  tab_spanner(
    label = md('T'),
    columns = contains('T')
  ) %>%
  tab_spanner(
    label = md('F'),
    columns = contains('F')
  ) %>%
  tab_spanner(
    label = md('Forced Convergence'),
    columns = contains('T') | contains('F')
  ) %>%
  cols_align(
    align = 'left',
    columns = c(where(is.factor), where(is.character))
  ) %>%
  cols_label(
  bounds = 'Maximum Iterations'  
  )%>%
  fmt_number(decimals = 3)
```

```{r}
cfi_40_table
```

```{r}
gt::gtsave(data = cfi_40_table, filename = 'cfi_40_table.docx', path="Tables")
```

```{r}
# wider table
srmr_10_wider <- srmr_10 %>%
  select(- frequency) %>% # removing the frequency column
  pivot_wider(names_from = c(conv, mlit),
  values_from = percentages, names_expand = T) %>%
  relocate(model) %>% # interchanging the first column with the model column
  mutate(
  ident = as.character(ident),
  model = as.character(model), 
  bounds = paste0('Bounds: ', bounds)
  )
```

```{r}
# the actual names
actual_names <- colnames(srmr_10_wider)

# new names
new_names <- actual_names %>%
  str_remove('(F|T)_') %>%
  str_to_title()

names(new_names) <- actual_names
```

```{r}
# table
srmr_10_table <- srmr_10_wider %>%
  gt(groupname_col = 'model', rowname_col = 'ident') %>% 
  cols_label(.list = new_names) %>%
  tab_spanner(
    label = md('T'),
    columns = contains('T')
  ) %>%
  tab_spanner(
    label = md('F'),
    columns = contains('F')
  ) %>%
  tab_spanner(
    label = md('Forced Convergence'),
    columns = contains('T') | contains('F')
  ) %>%
  cols_align(
    align = 'left',
    columns = c(where(is.factor), where(is.character))
  ) %>%
  cols_label(
  bounds = 'Maximum Iterations'  
  )%>%
  fmt_number(decimals = 3)
```

```{r}
srmr_10_table
```

```{r}
gt::gtsave(data = srmr_10_table, filename = 'srmr_10_table.docx', path="Tables")
```

```{r}
# wider table
srmr_09_wider <- srmr_09 %>%
  select(- frequency) %>% # removing the frequency column
  pivot_wider(names_from = c(conv, mlit),
  values_from = percentages, names_expand = T) %>%
  relocate(model) %>% # interchanging the first column with the model column
  mutate(
  ident = as.character(ident),
  model = as.character(model), 
  bounds = paste0('Bounds: ', bounds)
  )
```

```{r}
# the actual names
actual_names <- colnames(srmr_09_wider)

# new names
new_names <- actual_names %>%
  str_remove('(F|T)_') %>%
  str_to_title()

names(new_names) <- actual_names
```

```{r}
# table
srmr_09_table <- srmr_09_wider %>%
  gt(groupname_col = 'model', rowname_col = 'ident') %>% 
  cols_label(.list = new_names) %>%
  tab_spanner(
    label = md('T'),
    columns = contains('T')
  ) %>%
  tab_spanner(
    label = md('F'),
    columns = contains('F')
  ) %>%
  tab_spanner(
    label = md('Forced Convergence'),
    columns = contains('T') | contains('F')
  ) %>%
  cols_align(
    align = 'left',
    columns = c(where(is.factor), where(is.character))
  ) %>%
  cols_label(
  bounds = 'Maximum Iterations'  
  )%>%
  fmt_number(decimals = 3)
```

```{r}
srmr_09_table
```

```{r}
gt::gtsave(data = srmr_09_table, filename = 'srmr_09_table.docx', path="Tables")
```

```{r}
# wider table
srmr_08_wider <- srmr_08 %>%
  select(- frequency) %>% # removing the frequency column
  pivot_wider(names_from = c(conv, mlit),
  values_from = percentages, names_expand = T) %>%
  relocate(model) %>% # interchanging the first column with the model column
  mutate(
  ident = as.character(ident),
  model = as.character(model), 
  bounds = paste0('Bounds: ', bounds)
  )
```

```{r}
# the actual names
actual_names <- colnames(srmr_08_wider)

# new names
new_names <- actual_names %>%
  str_remove('(F|T)_') %>%
  str_to_title()

names(new_names) <- actual_names
```

```{r}
# table
srmr_08_table <- srmr_08_wider %>%
  gt(groupname_col = 'model', rowname_col = 'ident') %>% 
  cols_label(.list = new_names) %>%
  tab_spanner(
    label = md('T'),
    columns = contains('T')
  ) %>%
  tab_spanner(
    label = md('F'),
    columns = contains('F')
  ) %>%
  tab_spanner(
    label = md('Forced Convergence'),
    columns = contains('T') | contains('F')
  ) %>%
  cols_align(
    align = 'left',
    columns = c(where(is.factor), where(is.character))
  ) %>%
  cols_label(
  bounds = 'Maximum Iterations'  
  )%>%
  fmt_number(decimals = 3)
```

```{r}
srmr_08_table
```

```{r}
gt::gtsave(data = srmr_08_table, filename = 'srmr_08_table.docx', path="Tables")
```

```{r}
# wider table
rmsea_25_wider <- rmsea_25 %>%
  select(- frequency) %>% # removing the frequency column
  pivot_wider(names_from = c(conv, mlit),
  values_from = percentages, names_expand = T) %>%
  relocate(model) %>% # interchanging the first column with the model column
  mutate(
  ident = as.character(ident),
  model = as.character(model), 
  bounds = paste0('Bounds: ', bounds)
  )
```

```{r}
# the actual names
actual_names <- colnames(rmsea_25_wider)

# new names
new_names <- actual_names %>%
  str_remove('(F|T)_') %>%
  str_to_title()

names(new_names) <- actual_names
```

```{r}
# table
rmsea_25_table <- rmsea_25_wider %>%
  gt(groupname_col = 'model', rowname_col = 'ident') %>% 
  cols_label(.list = new_names) %>%
  tab_spanner(
    label = md('T'),
    columns = contains('T')
  ) %>%
  tab_spanner(
    label = md('F'),
    columns = contains('F')
  ) %>%
  tab_spanner(
    label = md('Forced Convergence'),
    columns = contains('T') | contains('F')
  ) %>%
  cols_align(
    align = 'left',
    columns = c(where(is.factor), where(is.character))
  ) %>%
  cols_label(
  bounds = 'Maximum Iterations'  
  )%>%
  fmt_number(decimals = 3)
```

```{r}
rmsea_25_table
```

```{r}
gt::gtsave(data = rmsea_25_table, filename = 'rmsea_25_table.docx', path="Tables")
```

```{r}
# wider table
rmsea_27_wider <- rmsea_27 %>%
  select(- frequency) %>% # removing the frequency column
  pivot_wider(names_from = c(conv, mlit),
  values_from = percentages, names_expand = T) %>%
  relocate(model) %>% # interchanging the first column with the model column
  mutate(
  ident = as.character(ident),
  model = as.character(model), 
  bounds = paste0('Bounds: ', bounds)
  )
```

```{r}
# the actual names
actual_names <- colnames(rmsea_27_wider)

# new names
new_names <- actual_names %>%
  str_remove('(F|T)_') %>%
  str_to_title()

names(new_names) <- actual_names
```

```{r}
# table
rmsea_27_table <- rmsea_27_wider %>%
  gt(groupname_col = 'model', rowname_col = 'ident') %>% 
  cols_label(.list = new_names) %>%
  tab_spanner(
    label = md('T'),
    columns = contains('T')
  ) %>%
  tab_spanner(
    label = md('F'),
    columns = contains('F')
  ) %>%
  tab_spanner(
    label = md('Forced Convergence'),
    columns = contains('T') | contains('F')
  ) %>%
  cols_align(
    align = 'left',
    columns = c(where(is.factor), where(is.character))
  ) %>%
  cols_label(
  bounds = 'Maximum Iterations'  
  )%>%
  fmt_number(decimals = 3)
```

```{r}
rmsea_27_table
```

```{r}
gt::gtsave(data = rmsea_27_table, filename = 'rmsea_27_table.docx', path="Tables")
```

```{r}
# wider table
rmsea_25_wider <- rmsea_25 %>%
  select(- frequency) %>% # removing the frequency column
  pivot_wider(names_from = c(conv, mlit),
  values_from = percentages, names_expand = T) %>%
  relocate(model) %>% # interchanging the first column with the model column
  mutate(
  ident = as.character(ident),
  model = as.character(model), 
  bounds = paste0('Bounds: ', bounds)
  )
```

```{r}
# the actual names
actual_names <- colnames(rmsea_25_wider)

# new names
new_names <- actual_names %>%
  str_remove('(F|T)_') %>%
  str_to_title()

names(new_names) <- actual_names
```

```{r}
# table
rmsea_25_table <- rmsea_25_wider %>%
  gt(groupname_col = 'model', rowname_col = 'ident') %>% 
  cols_label(.list = new_names) %>%
  tab_spanner(
    label = md('T'),
    columns = contains('T')
  ) %>%
  tab_spanner(
    label = md('F'),
    columns = contains('F')
  ) %>%
  tab_spanner(
    label = md('Forced Convergence'),
    columns = contains('T') | contains('F')
  ) %>%
  cols_align(
    align = 'left',
    columns = c(where(is.factor), where(is.character))
  ) %>%
  cols_label(
  bounds = 'Maximum Iterations'  
  )%>%
  fmt_number(decimals = 3)
```

```{r}
rmsea_25_table
```

```{r}
gt::gtsave(data = rmsea_25_table, filename = 'rmsea_25_table.docx', path="Tables")
```

```{r}
# wider table
rmsea_30_wider <- rmsea_30 %>%
  select(- frequency) %>% # removing the frequency column
  pivot_wider(names_from = c(conv, mlit),
  values_from = percentages, names_expand = T) %>%
  relocate(model) %>% # interchanging the first column with the model column
  mutate(
  ident = as.character(ident),
  model = as.character(model), 
  bounds = paste0('Bounds: ', bounds)
  )
```

```{r}
# the actual names
actual_names <- colnames(rmsea_30_wider)

# new names
new_names <- actual_names %>%
  str_remove('(F|T)_') %>%
  str_to_title()

names(new_names) <- actual_names
```

```{r}
# table
rmsea_30_table <- rmsea_30_wider %>%
  gt(groupname_col = 'model', rowname_col = 'ident') %>% 
  cols_label(.list = new_names) %>%
  tab_spanner(
    label = md('T'),
    columns = contains('T')
  ) %>%
  tab_spanner(
    label = md('F'),
    columns = contains('F')
  ) %>%
  tab_spanner(
    label = md('Forced Convergence'),
    columns = contains('T') | contains('F')
  ) %>%
  cols_align(
    align = 'left',
    columns = c(where(is.factor), where(is.character))
  ) %>%
  cols_label(
  bounds = 'Maximum Iterations'  
  )%>%
  fmt_number(decimals = 3)
```

```{r}
rmsea_30_table
```

```{r}
gt::gtsave(data = rmsea_30_table, filename = 'rmsea_30_table.docx', path="Tables")
```

\newpage

### Convergence Tables

```{r}
# loading the convergence table and reshape it to wide format
convergence_table <- results_one %>%
  group_by(model, bounds, ident, mlit, conv) %>%
  summarize(
  # average convergence
  avg_con = mean(con) * 100,
  # average non-convergence
  avg_non_con = mean(non_con) * 100, .groups = 'keep'
  ) %>%
  select(- avg_non_con) %>%
  pivot_wider(names_from = c(conv, mlit),
  values_from = avg_con, names_expand = T) %>%
  relocate(model) %>% # interchanging the first column with the model column
  mutate(
  ident = as.character(ident),
  model = as.character(model), 
  bounds = paste0('Bounds: ', bounds)
  )
```

```{r}
# the actual names
actual_names <- colnames(convergence_table)

# new names
new_names <- actual_names %>%
  str_remove('(F|T)_') %>%
  str_to_title()

names(new_names) <- actual_names
```

```{r}
convergence_table <- convergence_table %>%
  gt(groupname_col = 'model', rowname_col = 'ident') %>% 
  cols_label(.list = new_names) %>%
  tab_spanner(
    label = md('T'),
    columns = contains('T')
  ) %>%
  tab_spanner(
    label = md('F'),
    columns = contains('F')
  ) %>%
  tab_spanner(
    label = md('Forced Convergence'),
    columns = contains('T') | contains('F')
  ) %>%
  cols_align(
    align = 'left',
    columns = c(where(is.factor), where(is.character))
  ) %>%
  cols_label(
  bounds = 'Maximum Iterations'  
  )%>%
  fmt_number(decimals = 3)
```

```{r}
gt::gtsave(data = convergence_table, filename = 'convergence.docx', path="Tables")
```

### Convergence Tables no force convergence

```{r}
# loading the convergence table and reshape it to wide format
convergence_table <- results_one %>%
  filter(conv == 'F') %>%
  group_by(model, bounds, ident, mlit, conv) %>%
  summarize(
  # average convergence
  avg_con = mean(con) * 100,
  # average non-convergence
  avg_non_con = mean(non_con) * 100, .groups = 'keep'
  ) %>%
  select(- avg_non_con) %>%
  pivot_wider(names_from =  mlit,
  values_from = avg_con, names_expand = T) %>%
  relocate(model) %>% # interchanging the first column with the model column
  mutate(
  ident = as.character(ident),
  model = as.character(model), 
  bounds = paste0('Bounds: ', bounds)
  )
```

```{r}
# the actual names
actual_names <- colnames(convergence_table)

# new names
new_names <- actual_names %>%
  str_remove('(F|T)_') %>%
  str_to_title()

names(new_names) <- actual_names
```

```{r}
convergence_table <- convergence_table %>%
  gt(groupname_col = 'model', rowname_col = 'ident') %>% 
  cols_label(.list = new_names) %>%
  tab_spanner(
    label = md('T'),
    columns = contains('T')
  ) %>%
  tab_spanner(
    label = md('F'),
    columns = contains('F')
  ) %>%
  tab_spanner(
    label = md('Forced Convergence'),
    columns = contains('T') | contains('F')
  ) %>%
  cols_align(
    align = 'left',
    columns = c(where(is.factor), where(is.character))
  ) %>%
  cols_label(
  bounds = 'Maximum Iterations'  
  )%>%
  fmt_number(decimals = 3)
```

```{r}
gt::gtsave(data = convergence_table, filename = 'convergence-no-force.docx', path="Tables")
```

\newpage

### Log-likelihoods

#### Fitting propensity analysis to accomodate for different models

```{r}
fitting_prop <- function(Data, fit.index = c('logl', 'cfi', 'srmr', 'rmsea'), threshold, conditions = study3_conditions,
              models = c(1, 2, 3)){
  
  # Number of observations (kept as original for reference; per-iteration R computed below)
  R <- nrow(Data[[1]])  
  
  # Container for results  
  res <- list()
  
  # Store percentage values 
  per <- list()
  
  # Storing frequencies
  freq <- list()
  
  # Fit indices loop
  for (i in seq_along(Data)) {  
    res[[i]] <- Data[[i]]
    
    ## ADDED: create a working copy (df) and optionally filter by 'model' column
    df <- res[[i]]                      # work on df (keeps original res intact)
    if ("model" %in% colnames(df) && !is.null(models)) {
      df <- df[df$model %in% models, , drop = FALSE]
    }
    
    ## UPDATED: use the filtered-data-frame 'df' to find fit column and compute counts
    # Matching the column index for fit index
    fit.column <- which(colnames(df) == fit.index)
    
    if (length(fit.column) == 0) {
      stop(paste("Column", fit.index, "not found in dataset", i))
    }
    
    # denominator after optional filtering
    R_i <- nrow(df)
    
    if (fit.index == "cfi" & models %in% c(1, 2, 3))  { 
      
      # Calculate the proportion of values greater than the threshold
      results <- rev(table(df[,fit.column] > threshold, useNA = 'always'))
      
    } else if (fit.index %in% c('srmr','rmsea') & models %in% c(1, 2, 3)){  
      
      # Calculate the proportion of values less than the threshold
      results <- rev(table(df[,fit.column] < threshold, useNA = 'always'))
    
    # log-likelihood  
    } else {
      
      # Calculate the proportion of values less than the threshold
      results <- rev(table(df[,fit.column] > threshold, useNA = 'always'))
      
    }    
    
    # Ensure "TRUE" exists in results; otherwise, assign 0
    results_true <- ifelse("TRUE" %in% names(results), results['TRUE'], 0)
    
    # Saving the frequencies
    freq[[i]] <- results_true
    
    # Calculate percentages and saving them (use R_i so it reflects filtered rows)
    per[[i]] <- if (R_i > 0) (results_true / R_i) * 100 else 0
  }
  
  # Return the results as data frame
  dat <- data.frame('frequency' = unlist(freq), 'percentages' = unlist(per))
  
  # adding the conditions
  dat <- bind_cols(dat, conditions)
  
  # output
  return(dat)
  
}

```
