---
title: "Simulation III: All Correlations Analysis"
author: "Tive Khumalo (M.A),  Sonja Winter (Ph.D), Wes Bonifay (Ph.D), Brian Keller (Ph.D) & Hyejin Shim (Ph.D)"
format: pdf
editor: visual
geometry: a2paper
---

```{r}
# loading the data set
load(here::here("Online-Supplement","Data-Files","output_all_3.RData"))
```

- Since we have 48 models we will first assess convergence across all 48 models using a simple function that is shown below.

```{r}
# non-convergence
non_con <- sapply(output, function(x) mean(is.na(x)))

# convergence 
con <- 1 - non_con

# Grid of conditions that we can use for post-processing ----
study3_conditions <- expand.grid(model = 1:3, 
                                 bounds = c("none", "pos.var"),
                                 ident = c("refmarker", "unitvar"),
                                 mlit = c(150, 1500),
                                 conv = c("F", "T"))

# models as factors
study3_conditions$model <- factor(study3_conditions$model)
```

```{r warning=FALSE, message=FALSE}
# merging
results_one <- cbind(study3_conditions, con, non_con)


# loading the tidyverse package
library(tidyverse)

# average convergence and non-convergence
results_one %>%
  group_by(model) %>%
  summarize(
  # average convergence
  avg_con = mean(con) * 100,
  # average non-convergence
  avg_non_con = mean(non_con) * 100
  )
```

- On average model 1 had the highest convergence rate, 73.57(26.43), followed by model 2 with 68.44(31.56) and model 3 had the lowest average convergence rate, 66.99(33.01).

- Now we will look at the convergence rates across our conditions.

```{r}
# average convergence and non-convergence
results_one %>%
  group_by(model, bounds, ident, mlit, conv) %>%
  summarize(
  # average convergence
  avg_con = mean(con) * 100,
  # average non-convergence
  avg_non_con = mean(non_con) * 100, .groups = 'keep'
  ) %>%
  filter(avg_con != 1.0 & avg_non_con != 0)
```

```{r cells with low convergence}
# filter models with convergences lower or equal to 5%
results_one |>
  select(-non_con) |>
  filter(con <= .05)

```

```{r}
# number of conditions
num_con <- nrow(study3_conditions)

# number of data frames in the output
k <- length(output)

# check if the above is equal
if(k != num_con){
  stop('error k and num_con should be the same')
}

# container to save the results
output_conditions <- list()

for(i in 1:k){
  output_conditions[[i]] <- bind_cols(output[[i]], study3_conditions[i,])
  
}



# saving the dataset#
save(output_conditions, file = here::here("Online-Supplement","Data-Files", "output_all_3_conditions.RData"))
```

```{r}
# loading the data
load(here::here("Online-Supplement","Data-Files", "output_all_3_conditions.RData"))
```

### Fitting propensity analysis

```{r}
fitting_prop <- function(Data, fit.index = c('logl', 'cfi', 'srmr', 'rmsea'), threshold, conditions = study3_conditions){
  
# Number of observations
R <- nrow(Data[[1]])  
  
# Container for results  
res <- list()

# Store percentage values 
per <- list()

# Storing frequencies
freq <- list()
  
# Fit indices loop
for (i in seq_along(Data)) {  
  
res[[i]] <- Data[[i]]
    
# Matching the column index for fit index
fit.column <- which(colnames(res[[i]]) == fit.index)
    
if (length(fit.column) == 0) {
 stop(paste("Column", fit.index, "not found in dataset", i))
}
    
if (fit.index == "cfi") { 
  
# Calculate the proportion of values greater than the threshold
  results <- rev(table(res[[i]][,fit.column] > threshold, useNA = 'always'))
  
}else{  
  
# Calculate the proportion of values less than the threshold
  results <- rev(table(res[[i]][,fit.column] < threshold, useNA = 'always'))

}    

# Ensure "TRUE" exists in results; otherwise, assign 0
results_true <- ifelse("TRUE" %in% names(results), results['TRUE'], 0)
    
# Saving the frequencies
freq[[i]] <- results_true
    
# Calculate percentages and saving them
per[[i]] <- (results_true / R) * 100
  }
  
# Return the results as data frame
dat <- data.frame('frequency' = unlist(freq), 'percentages' = unlist(per))

# adding the conditions
dat <- bind_cols(dat, conditions)

# output
return(dat)

}
```

\newpage

**CFI**

```{r}
# cfi > .30
cfi_30 <- fitting_prop(Data = output_conditions, fit.index = 'cfi', threshold = .30)
```

```{r}
# cfi > .20
cfi_20 <- fitting_prop(Data = output_conditions, fit.index = 'cfi', threshold = .20)
```

```{r}
# cfi > .10
cfi_10 <- fitting_prop(Data = output_conditions, fit.index = 'cfi', threshold = .10)
```

\newpage

**SRMR**

```{r}
# srmr < .17
srmr_17 <- fitting_prop(Data = output_conditions, fit.index = 'srmr', threshold = .17)
```

```{r}
# srmr < .15
srmr_15 <- fitting_prop(Data = output_conditions, fit.index = 'srmr', threshold = .15)
```

```{r}
# srmr < .10
srmr_10 <- fitting_prop(Data = output_conditions, fit.index = 'srmr', threshold = .10)
```

\newpage

**RMSEA**

```{r}
# rmsea < .30
rmsea_30 <- fitting_prop(Data = output_conditions, fit.index = 'rmsea', threshold = .30)
```

```{r}
# rmsea < .27
rmsea_27 <- fitting_prop(Data = output_conditions, fit.index = 'rmsea', threshold = .27)
```

```{r}
# rmsea < .25
rmsea_25 <- fitting_prop(Data = output_conditions, fit.index = 'rmsea', threshold = .25)
```

\newpage

### Tables

**CFI**

```{r}
# loading gt
library(gt)

# wider table
cfi_30_wider <- cfi_30 %>%
  select(- frequency) %>% # removing the frequency column
  pivot_wider(names_from = c(conv, mlit),
  values_from = percentages, names_expand = T) %>%
  relocate(model) %>% # interchanging the first column with the model column
  mutate(
  ident = as.character(ident),
  model = as.character(model), 
  bounds = paste0('Bounds: ', bounds)
  )
```

```{r}
# the actual names
actual_names <- colnames(cfi_30_wider)

# new names
new_names <- actual_names %>%
  str_remove('(F|T)_') %>%
  str_to_title()

names(new_names) <- actual_names
```

```{r}
# table
cfi_30_table <- cfi_30_wider %>%
  gt(groupname_col = 'model', rowname_col = 'ident') %>% 
  cols_label(.list = new_names) %>%
  tab_spanner(
    label = md('T'),
    columns = contains('T')
  ) %>%
  tab_spanner(
    label = md('F'),
    columns = contains('F')
  ) %>%
  tab_spanner(
    label = md('Forced Convergence'),
    columns = contains('T') | contains('F')
  ) %>%
  cols_align(
    align = 'left',
    columns = c(where(is.factor), where(is.character))
  ) %>%
  cols_label(
  bounds = 'Maximum Iterations'  
  )%>%
  fmt_number(decimals = 3)
```

```{r}
cfi_30_table
```

```{r}
gt::gtsave(data = cfi_30_table, filename = 'cfi_30_table.docx',
path = here::here("Online-Supplement","Tables"))
```

```{r}
# wider table
cfi_20_wider <- cfi_20 %>%
  select(- frequency) %>% # removing the frequency column
  pivot_wider(names_from = c(conv, mlit),
  values_from = percentages, names_expand = T) %>%
  relocate(model) %>% # interchanging the first column with the model column
  mutate(
  ident = as.character(ident),
  model = as.character(model), 
  bounds = paste0('Bounds: ', bounds)
  )
```

```{r}
# the actual names
actual_names <- colnames(cfi_20_wider)

# new names
new_names <- actual_names %>%
  str_remove('(F|T)_') %>%
  str_to_title()

names(new_names) <- actual_names
```

```{r}
# table
cfi_20_table <- cfi_20_wider %>%
  gt(groupname_col = 'model', rowname_col = 'ident') %>% 
  cols_label(.list = new_names) %>%
  tab_spanner(
    label = md('T'),
    columns = contains('T')
  ) %>%
  tab_spanner(
    label = md('F'),
    columns = contains('F')
  ) %>%
  tab_spanner(
    label = md('Forced Convergence'),
    columns = contains('T') | contains('F')
  ) %>%
  cols_align(
    align = 'left',
    columns = c(where(is.factor), where(is.character))
  ) %>%
  cols_label(
  bounds = 'Maximum Iterations'  
  )%>%
  fmt_number(decimals = 3)
```

```{r}
cfi_20_table
```

```{r}
gt::gtsave(data = cfi_20_table, filename = 'cfi_20_table.docx', 
path = here::here("Online-Supplement","Tables"))
```

```{r}
# wider table
cfi_10_wider <- cfi_10 %>%
  select(- frequency) %>% # removing the frequency column
  pivot_wider(names_from = c(conv, mlit),
  values_from = percentages, names_expand = T) %>%
  relocate(model) %>% # interchanging the first column with the model column
  mutate(
  ident = as.character(ident),
  model = as.character(model), 
  bounds = paste0('Bounds: ', bounds)
  )
```

```{r}
# the actual names
actual_names <- colnames(cfi_10_wider)

# new names
new_names <- actual_names %>%
  str_remove('(F|T)_') %>%
  str_to_title()

names(new_names) <- actual_names
```

```{r}
# table
cfi_10_table <- cfi_10_wider %>%
  gt(groupname_col = 'model', rowname_col = 'ident') %>% 
  cols_label(.list = new_names) %>%
  tab_spanner(
    label = md('T'),
    columns = contains('T')
  ) %>%
  tab_spanner(
    label = md('F'),
    columns = contains('F')
  ) %>%
  tab_spanner(
    label = md('Forced Convergence'),
    columns = contains('T') | contains('F')
  ) %>%
  cols_align(
    align = 'left',
    columns = c(where(is.factor), where(is.character))
  ) %>%
  cols_label(
  bounds = 'Maximum Iterations'  
  )%>%
  fmt_number(decimals = 3)
```

```{r}
cfi_10_table
```

```{r}
gt::gtsave(data = cfi_10_table, filename = 'cfi_10_table.docx', 
path = here::here("Online-Supplement","Tables"))
```

```{r}
# wider table
srmr_10_wider <- srmr_10 %>%
  select(- frequency) %>% # removing the frequency column
  pivot_wider(names_from = c(conv, mlit),
  values_from = percentages, names_expand = T) %>%
  relocate(model) %>% # interchanging the first column with the model column
  mutate(
  ident = as.character(ident),
  model = as.character(model), 
  bounds = paste0('Bounds: ', bounds)
  )
```

```{r}
# the actual names
actual_names <- colnames(srmr_10_wider)

# new names
new_names <- actual_names %>%
  str_remove('(F|T)_') %>%
  str_to_title()

names(new_names) <- actual_names
```

```{r}
# table
srmr_10_table <- srmr_10_wider %>%
  gt(groupname_col = 'model', rowname_col = 'ident') %>% 
  cols_label(.list = new_names) %>%
  tab_spanner(
    label = md('T'),
    columns = contains('T')
  ) %>%
  tab_spanner(
    label = md('F'),
    columns = contains('F')
  ) %>%
  tab_spanner(
    label = md('Forced Convergence'),
    columns = contains('T') | contains('F')
  ) %>%
  cols_align(
    align = 'left',
    columns = c(where(is.factor), where(is.character))
  ) %>%
  cols_label(
  bounds = 'Maximum Iterations'  
  )%>%
  fmt_number(decimals = 3)
```

```{r}
srmr_10_table
```

```{r}
gt::gtsave(data = srmr_10_table, filename = 'srmr_10_table.docx', 
path = here::here("Online-Supplement","Tables"))
```

```{r}
# wider table
srmr_15_wider <- srmr_15 %>%
  select(- frequency) %>% # removing the frequency column
  pivot_wider(names_from = c(conv, mlit),
  values_from = percentages, names_expand = T) %>%
  relocate(model) %>% # interchanging the first column with the model column
  mutate(
  ident = as.character(ident),
  model = as.character(model), 
  bounds = paste0('Bounds: ', bounds)
  )
```

```{r}
# the actual names
actual_names <- colnames(srmr_15_wider)

# new names
new_names <- actual_names %>%
  str_remove('(F|T)_') %>%
  str_to_title()

names(new_names) <- actual_names
```

```{r}
# table
srmr_15_table <- srmr_15_wider %>%
  gt(groupname_col = 'model', rowname_col = 'ident') %>% 
  cols_label(.list = new_names) %>%
  tab_spanner(
    label = md('T'),
    columns = contains('T')
  ) %>%
  tab_spanner(
    label = md('F'),
    columns = contains('F')
  ) %>%
  tab_spanner(
    label = md('Forced Convergence'),
    columns = contains('T') | contains('F')
  ) %>%
  cols_align(
    align = 'left',
    columns = c(where(is.factor), where(is.character))
  ) %>%
  cols_label(
  bounds = 'Maximum Iterations'  
  )%>%
  fmt_number(decimals = 3)
```

```{r}
srmr_15_table
```

```{r}
gt::gtsave(data = srmr_15_table, filename = 'srmr_15_table.docx', 
path = here::here("Online-Supplement","Tables"))
```

```{r}

# wider table
srmr_17_wider <- srmr_17 %>%
  select(- frequency) %>% # removing the frequency column
  pivot_wider(names_from = c(conv, mlit),
  values_from = percentages, names_expand = T) %>%
  relocate(model) %>% # interchanging the first column with the model column
  mutate(
  ident = as.character(ident),
  model = as.character(model), 
  bounds = paste0('Bounds: ', bounds)
  )
```

```{r}
# the actual names
actual_names <- colnames(srmr_17_wider)

# new names
new_names <- actual_names %>%
  str_remove('(F|T)_') %>%
  str_to_title()

names(new_names) <- actual_names
```

```{r}
# table
srmr_17_table <- srmr_17_wider %>%
  gt(groupname_col = 'model', rowname_col = 'ident') %>% 
  cols_label(.list = new_names) %>%
  tab_spanner(
    label = md('T'),
    columns = contains('T')
  ) %>%
  tab_spanner(
    label = md('F'),
    columns = contains('F')
  ) %>%
  tab_spanner(
    label = md('Forced Convergence'),
    columns = contains('T') | contains('F')
  ) %>%
  cols_align(
    align = 'left',
    columns = c(where(is.factor), where(is.character))
  ) %>%
  cols_label(
  bounds = 'Maximum Iterations'  
  )%>%
  fmt_number(decimals = 3)
```

```{r}
srmr_17_table
```

```{r}
gt::gtsave(data = srmr_17_table, filename = 'srmr_17_table.docx',
path = here::here("Online-Supplement","Tables"))
```

```{r}
# wider table
rmsea_25_wider <- rmsea_25 %>%
  select(- frequency) %>% # removing the frequency column
  pivot_wider(names_from = c(conv, mlit),
  values_from = percentages, names_expand = T) %>%
  relocate(model) %>% # interchanging the first column with the model column
  mutate(
  ident = as.character(ident),
  model = as.character(model), 
  bounds = paste0('Bounds: ', bounds)
  )
```

```{r}
# the actual names
actual_names <- colnames(rmsea_25_wider)

# new names
new_names <- actual_names %>%
  str_remove('(F|T)_') %>%
  str_to_title()

names(new_names) <- actual_names
```

```{r}
# table
rmsea_25_table <- rmsea_25_wider %>%
  gt(groupname_col = 'model', rowname_col = 'ident') %>% 
  cols_label(.list = new_names) %>%
  tab_spanner(
    label = md('T'),
    columns = contains('T')
  ) %>%
  tab_spanner(
    label = md('F'),
    columns = contains('F')
  ) %>%
  tab_spanner(
    label = md('Forced Convergence'),
    columns = contains('T') | contains('F')
  ) %>%
  cols_align(
    align = 'left',
    columns = c(where(is.factor), where(is.character))
  ) %>%
  cols_label(
  bounds = 'Maximum Iterations'  
  )%>%
  fmt_number(decimals = 3)
```

```{r}
rmsea_25_table
```

```{r}
gt::gtsave(data = rmsea_25_table, filename = 'rmsea_25_table.docx', 
path = here::here("Online-Supplement","Tables"))
```

```{r}
rmsea_27_wider <- rmsea_27 %>%
  select(- frequency) %>% # removing the frequency column
  pivot_wider(names_from = c(conv, mlit),
  values_from = percentages, names_expand = T) %>%
  relocate(model) %>% # interchanging the first column with the model column
  mutate(
  ident = as.character(ident),
  model = as.character(model), 
  bounds = paste0('Bounds: ', bounds)
  )
```

```{r}
# the actual names
actual_names <- colnames(rmsea_27_wider)

# new names
new_names <- actual_names %>%
  str_remove('(F|T)_') %>%
  str_to_title()

names(new_names) <- actual_names
```

```{r}
# table
rmsea_27_table <- rmsea_27_wider %>%
  gt(groupname_col = 'model', rowname_col = 'ident') %>% 
  cols_label(.list = new_names) %>%
  tab_spanner(
    label = md('T'),
    columns = contains('T')
  ) %>%
  tab_spanner(
    label = md('F'),
    columns = contains('F')
  ) %>%
  tab_spanner(
    label = md('Forced Convergence'),
    columns = contains('T') | contains('F')
  ) %>%
  cols_align(
    align = 'left',
    columns = c(where(is.factor), where(is.character))
  ) %>%
  cols_label(
  bounds = 'Maximum Iterations'  
  )%>%
  fmt_number(decimals = 3)
```

```{r}
rmsea_27_table
```

```{r}
gt::gtsave(data = rmsea_27_table, filename = 'rmsea_27_table.docx',
path = here::here("Online-Supplement","Tables"))
```

```{r}
# wider table
rmsea_30_wider <- rmsea_30 %>%
  select(- frequency) %>% # removing the frequency column
  pivot_wider(names_from = c(conv, mlit),
  values_from = percentages, names_expand = T) %>%
  relocate(model) %>% # interchanging the first column with the model column
  mutate(
  ident = as.character(ident),
  model = as.character(model), 
  bounds = paste0('Bounds: ', bounds)
  )
```

```{r}
# the actual names
actual_names <- colnames(rmsea_30_wider)

# new names
new_names <- actual_names %>%
  str_remove('(F|T)_') %>%
  str_to_title()

names(new_names) <- actual_names
```

```{r}
# table
rmsea_30_table <- rmsea_30_wider %>%
  gt(groupname_col = 'model', rowname_col = 'ident') %>% 
  cols_label(.list = new_names) %>%
  tab_spanner(
    label = md('T'),
    columns = contains('T')
  ) %>%
  tab_spanner(
    label = md('F'),
    columns = contains('F')
  ) %>%
  tab_spanner(
    label = md('Forced Convergence'),
    columns = contains('T') | contains('F')
  ) %>%
  cols_align(
    align = 'left',
    columns = c(where(is.factor), where(is.character))
  ) %>%
  cols_label(
  bounds = 'Maximum Iterations'  
  )%>%
  fmt_number(decimals = 3)
```

```{r}
rmsea_30_table
```

```{r}
gt::gtsave(data = rmsea_30_table, filename = 'rmsea_30_table.docx',
path = here::here("Online-Supplement","Tables"))
```

\newpage

### Convergence Tables

```{r}
# loading the convergence table and reshape it to wide format
convergence_table <- results_one %>%
  group_by(model, bounds, ident, mlit, conv) %>%
  summarize(
  # average convergence
  avg_con = mean(con) * 100,
  # average non-convergence
  avg_non_con = mean(non_con) * 100, .groups = 'keep'
  ) %>%
  select(- avg_non_con) %>%
  pivot_wider(names_from = c(conv, mlit),
  values_from = avg_con, names_expand = T) %>%
  relocate(model) %>% # interchanging the first column with the model column
  mutate(
  ident = as.character(ident),
  model = as.character(model), 
  bounds = paste0('Bounds: ', bounds)
  )
```

```{r}
# the actual names
actual_names <- colnames(convergence_table)

# new names
new_names <- actual_names %>%
  str_remove('(F|T)_') %>%
  str_to_title()

names(new_names) <- actual_names
```

```{r}
convergence_table <- convergence_table %>%
  gt(groupname_col = 'model', rowname_col = 'ident') %>% 
  cols_label(.list = new_names) %>%
  tab_spanner(
    label = md('T'),
    columns = contains('T')
  ) %>%
  tab_spanner(
    label = md('F'),
    columns = contains('F')
  ) %>%
  tab_spanner(
    label = md('Forced Convergence'),
    columns = contains('T') | contains('F')
  ) %>%
  cols_align(
    align = 'left',
    columns = c(where(is.factor), where(is.character))
  ) %>%
  cols_label(
  bounds = 'Maximum Iterations'  
  )%>%
  fmt_number(decimals = 3)
```

```{r}
gt::gtsave(data = convergence_table, filename = 'convergence.docx', 
ppath = here::here("Online-Supplement","Tables"))
```

### Convergence Tables no force convergence

```{r}
# loading the convergence table and reshape it to wide format
convergence_table <- results_one %>%
  filter(conv == 'F') %>%
  group_by(model, bounds, ident, mlit, conv) %>%
  summarize(
  # average convergence
  avg_con = mean(con) * 100,
  # average non-convergence
  avg_non_con = mean(non_con) * 100, .groups = 'keep'
  ) %>%
  select(- avg_non_con) %>%
  pivot_wider(names_from = mlit,
  values_from = avg_con, names_expand = T) %>%
  relocate(model) %>% # interchanging the first column with the model column
  mutate(
  ident = as.character(ident),
  model = as.character(model), 
  bounds = paste0('Bounds: ', bounds)
  )
```

```{r}
# the actual names
actual_names <- colnames(convergence_table)

# new names
new_names <- actual_names %>%
  str_remove('(F|T)_') %>%
  str_to_title()

names(new_names) <- actual_names
```

```{r}
convergence_table <- convergence_table %>%
  gt(groupname_col = 'model', rowname_col = 'ident') %>% 
  cols_label(.list = new_names) %>%
  tab_spanner(
    label = md('T'),
    columns = contains('T')
  ) %>%
  tab_spanner(
    label = md('F'),
    columns = contains('F')
  ) %>%
  tab_spanner(
    label = md('Forced Convergence'),
    columns = contains('T') | contains('F')
  ) %>%
  cols_align(
    align = 'left',
    columns = c(where(is.factor), where(is.character))
  ) %>%
  cols_label(
  bounds = 'Maximum Iterations'  
  )%>%
  fmt_number(decimals = 3)
```

```{r}
gt::gtsave(data = convergence_table, filename = 'convergence-no-force_all.docx', path = here::here("Online-Supplement","Tables"))
```

\newpage

### Log-likelihoods

```{r warning=FALSE, message=FALSE}
# average log-likelihoods

# container
avg_logl <- rep(0, length(output_conditions))

for(i in seq_along(output_conditions)){
  avg_logl[i] <- mean(output_conditions[[i]][,1], na.rm = T)
}

# converting the avg_logl to a data frame
avg_logl <- data.frame('means' = avg_logl)


# merging with the study conditions
logl_results <- bind_cols(avg_logl, study3_conditions)
```

```{r warning=FALSE, message=FALSE}
# reshaping the data
logl_wider <- logl_results %>%
  pivot_wider(names_from = c(conv, mlit),
  values_from = means, names_expand = T) %>%
  relocate(model) %>% # interchanging the first column with the model column
  mutate(
  ident = as.character(ident),
  model = as.character(model), 
  bounds = paste0('Bounds: ', bounds)
  )
```

```{r}
# the actual names
actual_names <- colnames(logl_wider)

# new names
new_names <- actual_names %>%
  str_remove('(F|T)_') %>%
  str_to_title()

names(new_names) <- actual_names
```

```{r}
logl_table <- logl_wider %>%
  gt(groupname_col = 'model', rowname_col = 'ident') %>% 
  cols_label(.list = new_names) %>%
  tab_spanner(
    label = md('T'),
    columns = contains('T')
  ) %>%
  tab_spanner(
    label = md('F'),
    columns = contains('F')
  ) %>%
  tab_spanner(
    label = md('Forced Convergence'),
    columns = contains('T') | contains('F')
  ) %>%
  cols_align(
    align = 'left',
    columns = c(where(is.factor), where(is.character))
  ) %>%
  cols_label(
  bounds = 'Maximum Iterations'  
  )%>%
  fmt_number(decimals = 3)
```

```{r}
logl_table
```

```{r}
gt::gtsave(data = logl_table, filename = 'loglike.docx',
path = here::here("Online-Supplement","Tables"))
```
